\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
changed matsim comparison in related works

OSM data has been used by traffic simulators in the past. MATSim is one such
multiagent simulator that focuses on performing large-scale simulations in a
relatively small amount of time \cite{balmer2009matsim}. Traffic demand is
supplied to MATSim in the form of \textit{plans} that an individual may intend
to follow in a given day. MATSim aims to iteratively improve these plans to
minimize traffic delays while minimizing the total amount of time by which
agents are late to their destinations. This goal is somewhat different from
that of AORTA, where the routes (demand) supplied by individuals is taken as is
and does not have a pre-determined ideal time of arrival. Rather than improving
agent routes, AORTA allows creating entirely different behaviors for both
vehicles and intersections in order to simulate a different environment instead
of optimizing plans for a society in a static environment \commentpk{I think
MIke made these changes last night, but I am not sure if the last few sentences
are clear to me}.

>>>>

OSM data has been used by traffic simulators in the past. MATSim is one such
multiagent simulator that focuses on performing large-scale simulations in a
relatively small amount of time \cite{balmer2009matsim}. Traffic demand is
supplied to MATSim in the form of \textit{plans} that an individual may intend
to follow in a given day. MATSim aims to improve these plans by attempting to
minimize the total amount of time by which individuals are late to their
destinations. This goal is somewhat different from that of AORTA, where the
routes (demand) supplied by individuals is taken as is, and each agent has a
specified destination at a given point in time. Instead, AORTA focuses on
vehicle behaviors and intersection policies that can help this agent reach its
destination faster.

% This goal is somewhat different from that of AORTA, where the
% routes (demand) supplied by individuals is taken as is and does not have a
% pre-determined ideal time of arrival. Rather than improving agent routes, AORTA
% allows creating entirely different behaviors for both vehicles and
% intersections in order to simulate a different environment instead of
% optimizing plans for a society in a static environment \commentpk{I think MIke
% made these changes last night, but I am not sure if the last few sentences are
% clear to me}.
